---
title: "course26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
data(diamonds)
names(diamonds)
ggplot(aes(x,price),data = diamonds)+ geom_point(alpha = 1/10)
```
get the correlation between price and x ,y ,z.
```{r}
with(diamonds,cor.test(price,depth))
# with(diamonds,cor.test(price,y))
# with(diamonds,cor.test(price,z))
```
plot a scatter between price and depth
```{r}
summary(diamonds$depth)
ggplot(data = diamonds, aes(x = depth, y = price)) + 
  geom_point(alpha = 1/100)+
  scale_x_continuous(limits = c(43,79),breaks = seq(43,79,2))

```
# Create a scatterplot of price vs carat
# and omit the top 1% of price and carat
# values.
```{r}
ggplot(aes(carat,price),data = diamonds)+ geom_point(alpha=1/20)+
  ylim(0,quantile(diamonds$price,0.99))+
  xlim(0,quantile(diamonds$carat,0.99))
```
# Create a scatterplot of price vs. volume (x * y * z).
# This is a very rough approximation for a diamond's volume.

# Create a new variable for volume in the diamonds data frame.
# This will be useful in a later exercise.

```{r}
library(dplyr)
diamonds <- mutate(diamonds,volume = x*y*z)
ggplot(aes(volume,price),data = diamonds)+
  geom_point()
library(plyr)
count(diamonds$volume==0)
```
# Subset the data to exclude diamonds with a volume
# greater than or equal to 800. Also, exclude diamonds
# with a volume of 0. Adjust the transparency of the
# points and add a linear model to the plot. (See the
# Instructor Notes or look up the documentation of
# geom_smooth() for more details about smoothers.)

```{r}
ggplot(aes(volume,price),data = subset(diamonds,volume<800&&volume!=0))+
  geom_point(alpha =1/20)+
    geom_smooth(method = 'lm',color = 'red')
```
 Use the function dplyr package
# to create a new data frame containing
# info on diamonds by clarity.

# Name the data frame diamondsByClarity

# The data frame should contain the following
# variables in this order.

#       (1) mean_price
#       (2) median_price
#       (3) min_price
#       (4) max_price
#       (5) n

# where n is the number of diamonds in each
# level of clarity.

```{r}
library(plyr)
diamondsByClarity <- diamonds %>%
  group_by(clarity) %>%
  dplyr::summarise(mean_price = mean(price),
            median_price = median(price),
            min_price = min(price),
            max_price = max(price),
            n = n()) 
```
# We’ve created summary data frames with the mean price
# by clarity and color. You can run the code in R to
# verify what data is in the variables diamonds_mp_by_clarity
# and diamonds_mp_by_color.

# Your task is to write additional code to create two bar plots
# on one output image using the grid.arrange() function from the package
# gridExtra.
```{r}
library(gridExtra)

diamonds_by_color <- group_by(diamonds, color)
diamonds_mp_by_color <- dplyr::summarise(diamonds_by_color, mean_price = mean(price))
# ggplot(aes(x = color,y = price),data = diamonds)+ geom_histogram(color = 'blue',binwidth = 1)
# gg2 <- ggplot(aes(x = clarity, y = price),data = diamonds)+ geom_histogram(color = 'green',binwidth = 1)
# grid.arrange(gg1,gg2,ncol = 1)
g1 <- diamonds_mp_by_clarity$mean_price
names(g1) <- diamonds_mp_by_clarity$clarity
bar1 <- barplot(g1)
g2 <- diamonds_mp_by_color$mean_price
names(g2) <- diamonds_mp_by_color$color
bar2 <- barplot(g2,main = 'hhe')
grid.arrange(barplot(g1),barplot(g2),ncol =1)
```
