---
title: "course27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Create a histogram of diamond prices.
# Facet the histogram by diamond color
# and use cut to color the histogram bars.

```{r}
library(ggplot2)
data(diamonds)
ggplot(aes(x = price),data=diamonds)+
  geom_histogram()+facet_wrap(~color)
```
# Create a scatterplot of diamond price vs.
# table and color the points by the cut of
# the diamond.
```{r}
ggplot(aes(x = table,y = price),data = diamonds)+geom_point(aes(color = cut))+scale_x_continuous(breaks = seq(0,90,2))
```
# Create a scatterplot of diamond price vs.
# volume (x * y * z) and color the points by
# the clarity of diamonds. Use scale on the y-axis
# to take the log10 of price. You should also
# omit the top 1% of diamond volumes from the plot.

# Note: Volume is a very rough approximation of
# a diamond's actual volume.

# The plot should look something like this.
# http://i.imgur.com/excUpea.jpg

# Note: In the link, a color palette of type
# 'div' was used to color the scatterplot using
# scale_color_brewer(type = 'div')
```{r}
diamonds <- transform(diamonds,volume = x*y*z)
names(diamonds)
ggplot(aes(x= volume,y =price),data = diamonds)+
  geom_point(aes(color = clarity))+
  xlim(0,quantile(diamonds$volume,0.99))+
  scale_y_log10()+
  scale_color_brewer(type = 'div')
```
# Many interesting variables are derived from two or more others.
# For example, we might wonder how much of a person's network on
# a service like Facebook the user actively initiated. Two users
# with the same degree (or number of friends) might be very
# different if one initiated most of those connections on the
# service, while the other initiated very few. So it could be
# useful to consider this proportion of existing friendships that
# the user initiated. This might be a good predictor of how active
# a user is compared with their peers, or other traits, such as
# personality (i.e., is this person an extrovert?).

# Your task is to create a new variable called 'prop_initiated'
# in the Pseudo-Facebook data set. The variable should contain
# the proportion of friendships that the user initiated.
```{r}
pf <- read.csv('../pseudo_facebook.tsv',sep='\t')
pf <- transform(pf,prop_initiated=friendships_initiated/friend_count)
head(pf)
```
# Create a line graph of the median proportion of
# friendships initiated ('prop_initiated') vs.
# tenure and color the line segment by
# year_joined.bucket.

# Recall, we created year_joined.bucket in Lesson 5
# by first creating year_joined from the variable tenure.
# Then, we used the cut function on year_joined to create
# four bins or cohorts of users.

# (2004, 2009]
# (2009, 2011]
# (2011, 2012]
# (2012, 2014]
```{r}
pf <- transform(pf,year_joined = floor(2014-tenure/365))
pf$year_joined.bucket <- cut(pf$year_joined,breaks = c(2004,2009,2011,2012,2014))
ggplot(aes(x = tenure,y=prop_initiated),data = subset(pf,!is.na(year_joined.bucket)))+
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = median)
```

```{r}
ggplot(aes(x = tenure,y=prop_initiated),data = subset(pf,!is.na(year_joined.bucket)))+
  geom_smooth(aes(color = year_joined.bucket))
```
```{r}
library(dplyr)
names(pf)
pf.mean_friend <- pf %>%
  group_by(year_joined.bucket) %>%
  summarise(mean_friendships_initiated = mean(prop_initiated),
            count = n())%>%
  arrange(mean_friendships_initiated)
head(pf.mean_friend)
```
 Create a scatter plot of the price/carat ratio
# of diamonds. The variable x should be
# assigned to cut. The points should be colored
# by diamond color, and the plot should be
# faceted by clarity.

# The plot should look something like this.
# http://i.imgur.com/YzbWkHT.jpg.

# Note: In the link, a color palette of type
# 'div' was used to color the histogram using
# scale_color_brewer(type = 'div')

# This assignment is not graded and
# will be marked as correct when you submit.
```{r}
names(diamonds)
ggplot(aes(x =cut,y = price/carat),data = diamonds)+
  geom_point(aes(color = color))+
  facet_wrap(~clarity)+
  scale_color_brewer(type = 'div')
```

